Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-03 docs/ms.tex
Update ms.tex

In summary,We have presented a conceptually simple method for estimating
tangential shear , with carefully calculated uncertainty estimates.
This method is intrinsically cope with high noise levels on the input
data and naturally allows bad fit to be identified from the residuals
map. We have proposed an exceeding flexible model for intrinsic shape
distribution allows us to obtain the correct posterior distributions,
while avoiding making unsupported assumptions.The Gibbs sampler allows
us to sample the posterior distribution of shear in large number of
sky patches simultaneously and efficiently.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In summary,We have presented a conceptually hierachical inference
approach for weak lensing shear estimation, with carefully calculated 
uncertainty estimates.This method is intrinsically cope with high noise
levels on the input data and naturally allows bad fit to be identified 
from the residuals map. We have proposed an exceeding flexible model for 
intrinsic shape distribution allows us to obtain the correct posterior 
distributions, while avoiding making unsupported assumptions.The Gibbs
sampler allows us to sample the posterior distribution of shear in large number of
sky patches simultaneously and efficiently.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
